\section{Introduction}

Java 8 is one of the most significant upgrades to Java programming language
and framework in over a decade. It provides supports for functional
programming, a new JavaScript engine, new APIs for date time manipulation, a
new stream API, and more~\cite{newjdk}. There are several new key features of
Java 8 that can help make programs easier to read, write, and maintain
\cite{gyori2013}.

Among the new Java 8 features, lambda expressions are touted to be most
significant. Lambda expression simplify the development process by
facilitating functional programming. They also provide a concise way to write
anonymous inner classes and make it easier to iterate through, filter, and
exact data from a \lstinline{Collection}~\cite{lambdaqs}.

Eclipse\footnote{\url{http://eclipse.org}} is one of the most popular IDEs for
Java. While Eclipse has incorporated several Java 8 feature quick-fixes and
refactorings, there are still many features left to be done. For example, the
NetBeans IDE\footnote{\url{http://netbeans.org}} has a refactoring (originally
proposed by \citet{gyori2013}) that converts enhanced \lstinline{for} loops to
a lambda expression.  This paper discusses our ongoing work in exploring the
porting of such conversion mechanisms from NetBeans to the Eclipse IDE\@.
These will be manifested as a refactoring and a quick-fix\footnote{Quick-fixes
in Eclipse are content-assisted completions that help developers maintain and
improve their code.}, and will help Eclipse developers adapt the
functional-like programming model offered by Java 8. Furthermore, we are in
the process of exploring other Java 8 refactorings that do not currently exist
in any IDE\@.

According to \citet{gyori2013}, making such changes manually would require
changing approx.~1,700 line of non-commented, non-blank lines of code across
approx.~100 files per project, on average. With our plug-in, Eclipse
developers would not need to make these changes manually. 

We are currently developing an Eclipse plug-in that will detect enhanced
\lstinline{for} loops in Java code and will provide developers with different
ways to convert it into a lambda expression.  More details can be found in
Eclipse bug \#462725 (see
\url{http://bugs.eclipse.org/bugs/show_bug.cgi?id=462725}).
